Optimal (Multiway) Spatial Joins

### 2024-05-22 msj.tex
yufei

\begin{theorem} \label{thm:main-recur}
    For any $n \ge 1$, equipped with the algorithm $\A$ as described above, the $k$-SJ problem can be solved in
    \myeqn{
        O(k^3) \cdot \big( F_{k-1}(n, \out) + n \log n + \out \big)
        \label{eqn:main:reccurrence}
    }
    time using $O(n + \out)$ space, plus the worst-case space of $\A$ on any $(k-1)$-SJ instance with input size $n$ and output size $\out$.
\end{theorem}

@@

\begin{theorem} \label{thm:main-alg}
    For $k \ge 3$, we can settle $k$-SJ with a comparison-based algorithm in $O( c^k (k!)^3 \cdot (n \log n + \out))$ time and $O(k \cdot n + \out)$ space, where $c > 1$ is a positive constant.
\end{theorem}

When $k = O(1)$, the time and space complexities become $O(n \log n$ $+ \out)$ and $O(n + \out)$, as promised.

>>>>

\begin{theorem} \label{thm:main-recur}
    For any $n \ge 1$, equipped with the algorithm $\A$ as described above, the $k$-SJ problem can be solved in time
    \myeqn{
        O(k^3) \cdot \big( F_{k-1}(n, \out) + n \log n + \out \big).
        \label{eqn:main:reccurrence}
    }
%     time using $O(n + \out)$ space, plus the worst-case space of $\A$ on any $(k-1)$-SJ instance with input size $n$ and output size $\out$.
\end{theorem}

@@

\begin{theorem} \label{thm:main-alg}
    For $k \ge 3$, we can settle $k$-SJ with a comparison-based algorithm in $O( c^k (k!)^3 \cdot (n \log n + \out))$ time.
    %and $O(k \cdot n + \out)$ space, where $c > 1$ is a positive constant.
\end{theorem}

We will also prove that the space of our algorithm is $O(k \cdot n)$. When $k = O(1)$, the time and space complexities become $O(n \log n$ $+ \out)$ and $O(n + \out)$, as promised.
